Grove: A Convergent Collaborative Structure-Editor Calculus

### 2021-01-08 grove-paper.tex
Add notes about related work

@@

CRDTs

>>>>

We are using action based instead of tree diff

We have to deal with merge

We have to deal with edits from multiple people

@@

Collaborative Structure Editing

SmallTalk collaboration with images

TouchDevelop papers

\subsection{CRDTs}
(Are we a known CRDT?)

Bottom = Tombstone

https://www.waitingforcode.com/big-data-algorithms/conflict-free-replicated-data-types-flags-graphs-maps/read
 - Add-Remove Partial Order data type
 - 2P2P-Sets
 - Replicated Growable Array

 commutative replicated data types CmRDT
 convergent replicated data types, or CvRDTs
 Delta state CRDTs[12][13] (or simply Delta CRDTs

\url{https://en.wikipedia.org/wiki/Conflict-free_replicated_data_type}
 - LWW-Element-Set (Last-Write-Wins-Element-Set)
 - OR-Set (Observed-Remove Set)

PN-Set

https://medium.com/@amberovsky/crdt-conflict-free-replicated-data-types-b4bfc8459d26
 removeVertex() has priority, all incident edges are removed
 addEdge() has priority, all removed vertices are re-added
 Delay removeVertex() execution till all concurrent removeVertex() are executed.
First one is 2P2P-Set

textcomp Genealogical Symbols
\textborn
\textdied

2P-Sets
Anomaly: Creating a lone deleted vertex requires create and delete of otherwise unneeded edge
